Dismal Code: Studying the Evolution of Security Bugs

### 2013-02-07 docs/msr.tex
added another observation about bugless projects
added some measurements for severe security bugs

FindBugs separates software bugs into seven categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
Malicious Code}. Our early findings indicated that from the total number of the
artifacts, 4,270 of them contained at least one bug coming from the first category
and 45,145 from the second.

@@

5,601 - jar size - 17,505. Total Projects: 5601, Versions: 32689.

>>>>

\begin{table*}
\centering
\begin{center}
\leavevmode
	\begin{tabular}{l r}
	\hline
	Bug Description & Number of Artifacts\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1564\\
	{\sc pt}: absolute path traversal in servlet  & 92\\
	{\sc pt}: relative path traversal in servlet & 50\\
	{\sc sql}: nonconstant string passed to execute method on an {\sc sql} & 1817\\
	{\sc sql}: a prepared statement is generated from a nonconstant String & 1438\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
	\hline
	\end{tabular}
\caption{Number of Artifacts that Contain at Least One Severe Security Bug}
\label{tbl:sev}
\end{center}
\end{table*}

FindBugs separates software bugs into seven categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
Malicious Code}. From the total number of the artifacts, 4,270 of them contained
at least one bug coming from the first category
and 45,145 from the second. Another observation involves bugs that we call {\it
severe}. Such bugs are related to vulnerabilities due to the lack of user-input
validation. Table~\ref{tbl:sev}) presents the number of artifacts where at
least one of these bugs exists.

@@

An interesting observation is that 5,601 (31.99\%) projects, containing 32,689
artifacts (28.57\%), did not had any bugs at all. These cases involved small artifacts
with a minimum number of classes.
